Jug: Software for Reproducible Computation

### 2011-11-24 paper.tex
BLD Add necessary packages

\documentclass{article}

>>>>

\documentclass{article}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{python}
\usepackage[%
    natbib=true,%
    backend=biber,%
    backref=true,%
    citestyle=authoryear-comp,%
    bibstyle=authoryear,%
    maxbibnames=24,%
    maxcitenames=2,%
]{biblatex}

\hypersetup{%
    bookmarks=true,
    colorlinks=true,
    pdfauthor={Luis Pedro Coelho},
    citecolor=pondgreen,
    urlcolor=toastedchilipowder,
    linkcolor=toastedchilipowder,
}
\let\code\texttt
